---
format:
  pdf:
    papersize: letter
    geometry: margin=1in
    fontsize: 11pt
    mainfont: "Lato"
    linestretch: 1.15
    colorlinks: true
    urlcolor: black
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
#| include: false
library(tidyverse)
library(knitr)
library(kableExtra)
library(readr)

# Function to format publications with proper spacing and consistent font
format_publications <- function(data) {
  # Create citations
  citations <- data %>%
    arrange(desc(year)) %>%
    mutate(
      citation = paste0(
        authors, " (", year, "). ",
        title, ". ",
        journal
      )
    ) %>%
    pull(citation)
  
  # Create a data frame with blank rows between citations
  n_citations <- length(citations)
  formatted_df <- data.frame(
    citation = character(n_citations * 2 - 1)
  )
  
  # Fill in citations and blank rows
  for(i in 1:n_citations) {
    formatted_df$citation[2*i - 1] <- citations[i]
    if(i < n_citations) {
      formatted_df$citation[2*i] <- ""  # Insert blank row
    }
  }
  
  # Create table with kable
  formatted_df %>%
    kable(format = "pipe", 
          col.names = NULL) %>%
    kable_styling(font_size = 11,
                  full_width = TRUE,
                  bootstrap_options = "condensed") %>%
    column_spec(1, width = "6.5in")
}

# Function to create tables with consistent styling
create_table <- function(data, widths = NULL, align = NULL) {
  if (is.null(align)) {
    align = rep("l", ncol(data))
  }
  
  total_width <- sum(as.numeric(gsub("in", "", widths)))
  if (total_width > 6.5) {
    scaling_factor <- 6.5 / total_width
    widths <- paste0(as.numeric(gsub("in", "", widths)) * scaling_factor, "in")
  }
  
  tbl <- data %>%
    kable(format = "pipe", 
          align = align,
          col.names = NULL,
          escape = FALSE) %>%
    kable_styling(font_size = 11,
                  full_width = TRUE,
                  bootstrap_options = "condensed")
  
  if (!is.null(widths)) {
    for (i in 1:length(widths)) {
      tbl <- tbl %>% column_spec(i, width = widths[i])
    }
  }
  
  return(tbl)
}
```

::: {style="text-align: center; margin-bottom: 20pt"}
# GERARD CHUNG

Assistant Professor\
Department of Social Work\
National University of Singapore\
gerard\@nus.edu.sg | gerardchung.com

*Last Updated: December 2024*

:::

# EDUCATION

```{r}
tribble(
  ~Degree, ~Year, ~Institution, ~Location,
  "Ph.D. in Social Work", "2021", "University of North Carolina at Chapel Hill", "USA",
  "Master of Social Work", "2016", "National University of Singapore", "Singapore",
  "Bachelor of Arts (Social Work)", "2007", "National University of Singapore", "Singapore",
  "Graduate Diploma in Solution-focused Brief Therapy", "2011", "Edith Cowan University", "Australia"
) %>%
  arrange(desc(Year)) %>%
  create_table(widths = c("2.5in", "0.7in", "2.5in", "0.8in"))
```

# RESEARCH INTERESTS

-   Technologies, TECH, and AI in Social Work and Social Services
-   Parenting, Fathers, Stepfamily Devekioment
-   Social Work Practice with Parents and Children
-   Intervention Design, Development and Program Evaluation
-   Quantitative Research Methods and Adv Statistics
-   Large Text Data Analysis & Natural Language Processing

# ACADEMIC APPOINTMENTS

```{r}
tribble(
  ~Years, ~Position, ~Institution,
  "2023-present", "Assistant Professor, Department of Social Work", "National University of Singapore",
  "2022-2023", "Research Fellow", "A*STAR, Singapore",
  "2021-2023", "Research Fellow, Social Service Research Centre", "National University of Singapore"
) %>%
  create_table(widths = c("1.2in", "2.8in", "2.5in"))
```

# PUBLICATIONS

## Peer-Reviewed Journal Articles (First Author)

```{r}
read_csv("pub_published_table.csv") %>%
  format_publications()
```

## Peer-Reviewed Journal Articles (Co-Authored)

```{r}
read_csv("pub_coauthor_table.csv") %>%
  format_publications()
```

## Manuscripts Under Review

```{r}
read_csv("pub_inreview_table.csv") %>%
  format_publications()
```

# RESEARCH FUNDING AND AWARDS

```{r}
tribble(
  ~Year, ~Award, ~Institution, ~Amount,
  "2024", "Teaching Enhancement Grant", "NUS", "$15000",
  "2022", "Summer Institutes of Computational Social Science", "SICSS", "",
  "2021", "Injury Violence & Prevention Fellowship", "Injury Prevention Research Center, UNC", "$3,000",
  "2021", "Ee Peng Liang Scholar", "Ee Peng Liang Memorial Fund, NUS", "",
  "2020", "Injury Violence & Prevention Fellowship", "Injury Prevention Research Center, UNC", "$3,000",
  "2017", "Merit Assistantship (4 years funding)", "Graduate school, UNC", "",
  "2014", "Alice Goh Scholarship", "NUS", ""
) %>%
  arrange(desc(Year)) %>%
  create_table(widths = c("0.8in", "2.3in", "2.5in", "0.9in"))
```

# RESEARCH PROJECTS

```{r}
read_csv("research_proj.csv") %>%
  arrange(desc(year)) %>%
  select(`funder/collaborator`, project, year, role) %>%
  create_table(widths = c("1.3in", "3in", "0.8in", "1.4in"))
```

# TEACHING EXPERIENCE

## Primary Instructor

```{r}
tribble(
  ~Year, ~Course, ~Institution,
  "2025", "SW3224 Technology in Social Work", "NUS",
  "2025", "SW4103 Adv Research & Evaluation", "NUS",
  "2024", "SW4103 Adv Research & Evaluation", "NUS",
  "2023", "Practice Research I and II", "NUS",
  "2023", "SW4103 Adv Research & Evaluation", "NUS",
  "2022", "Research Skills for Social Service Professionals", "Social Service Research Centre",
  "2014", "Financial Cases: Assessment and Intervention", "Academy of Human Development Singapore"
) %>%
  create_table(widths = c("1in", "3in", "2.5in"))
```

## Graduate Student Instructor

```{r}
tribble(
  ~Year, ~Course, ~Institution,
  "2021", "SOWO 918: Applied Regression Analysis and GLM", "UNC Chapel Hill",
  "2020", "SOWO 911: Introduction to Social Statistics", "UNC Chapel Hill",
  "2019", "SOWO 500: Human Development in Context", "UNC Chapel Hill",
  "2018", "SOWO 800: Evaluation of Social Work Intervention", "UNC Chapel Hill"
) %>%
  create_table(widths = c("1in", "3in", "2.5in"))
```

# SERVICE AND PROFESSIONAL ACTIVITIES

## Research Consultancy

```{r}
tribble(
  ~Year, ~Organization, ~Role,
  "2021-2023", "Fei Yue Community Services", "Research Consultant",
  "2017-2018", "The Samaritans of Singapore SOS", "Research Consultant",
  "2017-2018", "Agency for Integrated Care AIC", "Research Consultant"
) %>%
  create_table(widths = c("1.2in", "3in", "2.3in"))
```

## Community Service

```{r}
tribble(
  ~Year, ~Role, ~Committee,
  "2024-", "Member", "SWITch SW & Informatics Champions",
  "2024-", "Advisor", "Fei Yue IRB",
) %>%
  create_table(widths = c("1.2in", "1.8in", "3.5in"))
```


## Editorial Service

```{r}
tribble(
  ~Year, ~Role, ~Journal,
  "2013-2017", "Editorial Assistant", "Asia Pacific Journal of Social Work and Development",
  "2020-present", "Ad Hoc Reviewer", "Journal of Child & Family Studies",
  "2020-present", "Ad Hoc Reviewer", "Journal of Family Violence",
  "2020-present", "Ad Hoc Reviewer", "Child & Family Social Work",
  "2020-present", "Ad Hoc Reviewer", "Family Relations",
  "2020-present", "Ad Hoc Reviewer", "Current Psychology",
  "2020-present", "Ad Hoc Reviewer", "Child & Youth Service Review"
) %>%
  create_table(widths = c("1.2in", "1.8in", "3.5in"))
```

# PROFESSIONAL REFERENCES

```{r}
tribble(
  ~Name, ~Title, ~Contact,
  "Mimi Chapman, Ph.D.", "Associate Dean for Doctoral Education; Frank A. Daniels Distinguished Professor", "mimi@email.unc.edu",
  "Chen Ding-Geng, Ph.D.", "Kuralt Distinguished Professor, School of Social Work; Professor in Biostatistics", "dinchen@email.unc.edu",
  "David Ansong, Ph.D.", "Kuralt Early Career Distinguished Associate Professor", "ansong@email.unc.edu",
  "Paul Lanier, Ph.D.", "Kuralt Distinguished Associate Professor; Associate Director, Jordan Institute of Families", "planier@email.unc.edu"
) %>%
  create_table(widths = c("2in", "3.5in", "1in"))
```
